### 2023-08-13 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics
of a multicomponent vesicle under strong confinement, which is a
ubiquitous configuration in biology when a cell squeezes through a small
channel. We refined the phase-field formulation
in~\citet{liu-mar-li-vee-low2017} with a new bending model that uses a
sigmoidal function for the bending stiffness to retain positiveness in
the bending modulus. The linear model~\cite{liu-mar-li-vee-low2017}
works well for a vesicle in free-space. However, under strong
confinement we find it necessary to enforce the condition that the
dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$
($\beta = b_{\min}/b_{\max}$) to avoid instability in membrane shapes
(see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a
multicomponent vesicle in two types of confinement: a stenosis channel
(\S~\ref{subsec:Stenosis}), and a contracting channel
(\S~\ref{subsec:Contraction}). For both confining geometries we varied
the reduced area $\alpha$, the floppy-to-stiffness ratio $\beta$, and
the initial distribution of lipid domains with a fixed Capillary number
$Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$. In
\S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
confinement ratio increases to a maximum of $3.60$ at the neck.
Consequently the dependence of the vesicle shape on the capillary number
is expected to be less sensitive according to results
in~\citet{aga-bir2020}. Finally the phase separation is assumed to occur
at a much faster time scale than vesicle relaxation with Peclet number
$Pe=1$.

As a multicomponent vesicle enters/leaves a closely-fitted stenosis,
coarsening of the lipid domains is expedited. However, inside the
stenosis, the strong confinement hinders the coarsening as both the
vesicle shape and the lipid domains remain more or less unaltered as the
vesicle moves through the stenosis. Once inside a stenosis, we define
the lubrication layer and its corresponding width to analyze the
mechanical coupling between the boundaries in lipid domain and the
planar shear flow inside the lubrication layer, which consists of a
quadratic component (due to pressure gradient in the thin film) and a
linear component (due to membrane motion in the tangential direction).
By analyzing these two components at various locations in the
lubrication layer, we first identified that tank treading along the
vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer
width on the two sides. We further elucidated the correlation between
the location of boundary between lipid domains, the Marangoni stress,
and the change of sign in the pressure gradient in the lubrication
layer. These results may be used to identify the lipid domains via the
visualization of the flow in the lubrication layer.

For a multicomponent vesicle squeezing through a constriction, we
simulated the passage of a vesicle with various initial configurations
of lipid domains. We found that, once the vesicle makes its passage, the
front of the vesicle is often stiffer than the back of the vesicle, with
a similar shape of a smaller curvature in the front than the curvature
in the back. This is also observed for a vesicle moving out of
confinement from a stenosis channel. Thus we propose a strong
confinement in combination with a sharp transition to a wider opening
can be used to produce phase-separated multicomponent vesicle with the
floppy lipid species in the back and the stiff lipid species in the
front of the vesicle.

Such asymmetry in lipid domain induced by strong confinement and sudden
release gives rise to a nonuniform tension distribution in the membrane,
with higher (?) tension in the front and lower (?) tension in the back.
This may have biophysical consequences in polarity developing of a
migrating cell.

>>>>

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics
of a multicomponent vesicle under strong confinement. The vesicle is an simplified model for a red blood cell (RBC), which has 
multiple lipid domains in its membrane and often has to squeeze through a small space.
We refined the phase-field formulation
in~\citet{liu-mar-li-vee-low2017} with a new bending model that uses a
sigmoidal function for the bending stiffness to retain positiveness in
the bending modulus. The linear model~\cite{liu-mar-li-vee-low2017}
works well for a vesicle in free-space. However, under strong
confinement we find it necessary to enforce the condition that the
dimensionless bending modulus $b(u)$ be in the range of $[\beta,1]$
($\beta = b_{\min}/b_{\max}$) to avoid instability in membrane shapes
(see \S~\ref{subsec:const_eq}). We focused on the hydrodynamics of a
multicomponent vesicle in two types of confinement: a stenosis channel
(\S~\ref{subsec:Stenosis}), and a contracting channel
(\S~\ref{subsec:Contraction}). For both confining geometries we varied
the reduced area $\alpha$  and
the initial distribution of lipid domains with a fixed floppy-to-stiff ratio $\beta=0.1$, 
a fixed Capillary number $Ca=0.25$ and a fixed Peclet number of the lipid dynamics $Pe=1$.

In \S~\ref{subsec:Stenosis} the confinement ratio (defined as $2R_0/W$) in
the stenosis is $1.67$, and in \S~\ref{subsec:Contraction} the
confinement ratio increases to a maximum of $3.60$ at the neck.
Consequently the dependence of the vesicle shape on the capillary number
is expected to be less sensitive according to results
in~\citet{aga-bir2020}. Finally the phase separation is assumed to occur
at a much faster time scale than vesicle relaxation with Peclet number
$Pe=1$.

As a multicomponent vesicle enters/leaves a closely-fitted stenosis,
coarsening of the lipid domains is expedited. However, inside the
stenosis, the strong confinement hinders the coarsening as both the
vesicle shape and the lipid domains remain more or less unaltered as the
vesicle moves through the stenosis. Once inside a stenosis, we define
the lubrication layer and its corresponding width to analyze the
mechanical coupling between the boundaries in lipid domain and the
planar shear flow inside the lubrication layer, which consists of a
quadratic component (due to pressure gradient in the thin film) and a
linear component (due to membrane motion in the tangential direction).
By analyzing these two components at various locations in the
lubrication layer, we first identified that tank treading along the
vesicle of $\alpha=0.4$ is due to the mismatch in lubrication layer
width between the two sides. We further elucidated the correlation between
the location of boundary between lipid domains, the Marangoni stress,
and the change of sign in the pressure gradient in the lubrication
layer. These results may be used to identify the lipid domains via the
visualization of the flow in the lubrication layer.

For a multicomponent vesicle squeezing through a constriction, we
simulated the passage of a vesicle with various initial configurations
of lipid domains. We found that, once the vesicle makes its passage, the
front of the vesicle is often stiffer than the back of the vesicle, with
a similar shape of a smaller curvature in the front than the curvature
in the back. This is also observed for a vesicle moving out of
confinement from a stenosis channel. Thus we propose that a strong
confinement followed by a sharp transition to a wider opening
can be used to produce phase-separated multicomponent vesicle with the
floppy lipid species in the back and the stiff lipid species in the
front of the vesicle.

Such asymmetry in lipid domain induced by strong confinement and sudden
release gives rise to a nonuniform tension distribution in the membrane,
with a higher tension (in magnitude) in the front and a smaller tension (in magnitude) in the back.
This may have biophysical consequences in polarity developing of a
migrating cell.
